THE FUNDAMENTAL CONNECTIONS BETWEEN CLASSICAL HAMILTONIAN MECHANICS, QUANTUM MECHANICS \\ AND INFORMATION ENTROPY

### 2019-09-18 Proceedings/2019-Quantum2019/CarcassiQuantum2019Proceedings.tex
Bibliography now works

\documentclass{ws-ijqi}
\usepackage{hyperref}
\usepackage[super,sort,compress]{cite}
\begin{document}

@@

\section{Introduction}
In a previous work we identified a small set of physical assumptions from which classical and quantum particle mechanics can be rederived. By assumptions here we mean simplifying conditions that our system is supposed to satisfy under the processes under study. Our work differs from others in that the starting points are physical assumptions about the system being studied (e.g whether the parts can be studied or whether the evolution is deterministic) and not some abstract mathematical or information theoretic considerations. It is also different in that both classical and quantum cases are derived on equal footing. That is, we have identified a single point where one assumption leads to the classical case while another lead to the quantum system.

>>>>

\documentclass{ws-ijqi}
\usepackage{hyperref}
\usepackage[super,sort,compress]{cite}
\usepackage{url}
\begin{document}

@@

\section{Introduction}
In a previous work\cite{Carc1} we identified a small set of physical assumptions from which classical and quantum particle mechanics can be rederived. By assumptions here we mean simplifying conditions that our system is supposed to satisfy under the processes under study. Our work differs from others in that the starting points are physical assumptions about the system being studied (e.g whether the parts can be studied or whether the evolution is deterministic) and not some abstract mathematical or information theoretic considerations. It is also different in that both classical and quantum cases are derived on equal footing. That is, we have identified a single point where one assumption leads to the classical case while another lead to the quantum system.
